---
title: "aer13_OriginalHomeworkCode_04"
author: "Abby_Robinson"
date: "10/20/2021"
output: html_document
---
#What's Your Malfunction? 

##[1] Write a simple R function, Z.prop.test(), that can perform one- or two-sample Z-tests for proportion data

```{r}
#p1 = estimated proportion based on sample 
#n1 = estimated sample size based on sample 

#p2 = estimated proportion based on second sample (if two-sample test)
#n2 = estimated sample size based on second sample (if two-sample test)

#p0 = (no default) as the expected value for the population proportion
  
x <- c(0,0,1,1,0,0,0,0,0,1,0,0,0,0,0,0,0,0,1,0,0,0,1,1,1,0,0,0,1)
length(x)
sum(x)

Z.prop.test = function(p1, n1, p0, phat){
  
Rule1 <- n1 * phat
Rule2 <- n1 * (1 - phat)

one.tail.p <- NULL

Z <- (phat-p0)/sqrt((p0*(1-p0))/n1)

one.tail.p <- round(pnorm(abs(Z),lower.tail = FALSE),3)

CI <- phat+c(-1,1)*qnorm(0.975)*sqrt(phat*(1-phat)/n1)

cat( "Rule of thumb 1 =", Rule1, "\n", 
     
"Rule of thumb 2 =", Rule2, "\n",

"z =",Z, "\n", 

"one-tailed probability =", one.tail.p, "\n",

"two-tailed probability =", 2*one.tail.p, "\n",

"CI =" ,CI,)}

Z.prop.test(8, 29, 14.5, 0.27)
```
ERROR: NaNs producedError in cat("Rule of thumb 1 =", Rule1, "\n", "Rule of thumb 2 =", Rule2, : argument is missing, with no default

Not sure how to code for the p values and test alternatives... this is a struggle... 


[2] The dataset from Kamilar and Cooper has in it a large number of variables related to life history and body size. For this exercise, the end aim is to fit a simple linear regression model to predict longevity (MaxLongevity_m) measured in months from species’ brain size (Brain_Size_Species_Mean) measured in grams. Do the following for both longevity~brain size and log(longevity)~log(brain size)

load libraries
```{r}
library(curl)
library(ggplot2)
library(gridExtra)
library(lmodel2)
```

```{r}
f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN588_Fall21/KamilarAndCooperData.csv")
data  <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
data
```

```{r}
m <- lm(MaxLongevity_m ~ Brain_Size_Species_Mean, data = data)
m
```

```{r}
g <- ggplot(data = data, aes(x = Brain_Size_Species_Mean, y = MaxLongevity_m))
g <- g + geom_point()
g <- g + geom_smooth(method = "lm", formula = y ~ x)
```

```{r}
df <- data.frame(x = data$MaxLongevity_m, y = data$Brain_Size_Species_Mean)
lm_eqn <- function(df){
    m <- lm(y ~ x, df);
    eq <- substitute(italic(y) == a + b %.% italic(x)*","~~italic(r)^2~"="~r2, 
         list(a = format(unname(coef(m)[1]), digits = 2),
              b = format(unname(coef(m)[2]), digits = 2),
             r2 = format(summary(m)$r.squared, digits = 3)))
    as.character(as.expression(eq));
}

p1 <- g + geom_text(x = 200, y = 400, label = lm_eqn(df), parse = TRUE)
p1
```
This isn't working.... I dont know why...

```{r}
ci <- confint(m, level = 0.90)  # using the results of lm()
ci
```

```{r}
library(manipulate)
```

```{r}
manipulate(slope.test(beta1), beta1 = slider(-1, 1, initial = 0, step = 0.005))
```


Log Model 

```{r}
longevity <- log(data$MaxLongevity_m)

brain.size <- log(data$Brain_Size_Species_Mean)

m2 <- lm(longevity ~ brain.size, data = data)
m2
```

```{r}
g <- ggplot(data = data, aes(x = brain.size, y = longevity))
g <- g + geom_point()
g <- g + geom_smooth(method = "lm", formula = y ~ x)
g
```

Using the log function distributes the datapoints more evenly across the graph. This is a data transformation technique that can be used to make data fit the normal distribution, yes? 


