---
title: "aer13_FinalHomeworkCode_04"
author: "Abby_Robinson"
date: "10/20/2021"
output: html_document
---
#What's Your Malfunction? 

##[1] Write a simple R function, Z.prop.test(), that can perform one- or two-sample Z-tests for proportion data

Function for z test 
```{r}
#p1 = estimated proportion based on sample 
#n1 = estimated sample size based on sample 

#p2 = estimated proportion based on second sample (if two-sample test)
#n2 = estimated sample size based on second sample (if two-sample test)

#p = (no default) as the expected value for the population proportion
  
Z.prop.test = function(p1, n1, p, p2, n2){
  
if(is.null(p2)){ 
  
one.tail.p <- NULL

rule_one <- (n1*p1)

rule_two <- (n1*(1-p1))

Z <- (p1-p)/sqrt((p*(1-p))/n1)

one.tail.p <- round(pnorm(abs(Z),lower.tail = FALSE),3)

CI <- p1+c(-1,1)*qnorm(0.975)*sqrt(p1*(1-p1)/n1)

p.value <- pnorm(-abs(Z))

cat("Rule One =", rule_one <- rule_one, "\n",
    "Rule Two =", rule_two <- rule_two, "\n",
    "Z_score =", Z <- Z, "\n", 
    "one_tailed =", one.tail.p <- one.tail.p, "\n", 
    "one_tailed_p_value =", p.value <- p.value, "\n",
    "two_tailed =", 2*one.tail.p, "\n",
    "two-tailed_p_value =", 2*p.value, "\n",
    "CI =", CI <- CI, "\n")

} else { 
  
Z.two.sample <- (p1-p2)/ sqrt((p*(1-p))*((1/n1)+(1/n2)))

CI.two.sample <- CI <- p2+c(-1,1)*qnorm(0.975)*sqrt(p2*(1-p2)/n2)

P.Value <- pnorm(-Z.two.sample)

cat( "Z_score =", Z.two.sample <- Z.two.sample, "\n", 
     "CI =", CI.two.sample <- CI.two.sample, "\n", 
     "P-Value =", P.Value <- P.Value, "\n")
}
  
}
```

Run one sample z test 
```{r}
Z.prop.test(0.276, 29, 0.5,p2=NULL, 0)
```

Run two sample 
```{r}
Z.prop.test(0.276, 29, 0.5, 0.35, 35)
```
So, in the above code, you need to set p2 = 0 for the funciton to run the one sample z test 

*^yes. I am a understanding that the rule_one and rule_two part are functioning to check for normal distribution (rule of thumb)? It is helpful to use "print" to give a message for when it doesn't fall in the distrbution, but maybe that is part of the cat() function that I am unaware of. You aren't setting p0 or "alternative" in your function, but the confidence intervals still seem to work*


[2] The dataset from Kamilar and Cooper has in it a large number of variables related to life history and body size. For this exercise, the end aim is to fit a simple linear regression model to predict longevity (MaxLongevity_m) measured in months from species’ brain size (Brain_Size_Species_Mean) measured in grams. Do the following for both longevity~brain size and log(longevity)~log(brain size)

load libraries
```{r}
library(curl)
library(ggplot2)
library(gridExtra)
library(lmodel2)
```

load dataset 
```{r}
f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN588_Fall21/KamilarAndCooperData.csv")
data  <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
data
```

linear regression model for longevity ~ brain size 

```{r}
m <- lm(MaxLongevity_m ~ Brain_Size_Species_Mean, data = data)
m
```

use ggplot to graph data and use geom_point and geom_smooth to superimpose fitted line, use geom_text to append the equation using the intercept and slope from the above output 

```{r}
g <- ggplot(data = data, aes(x = Brain_Size_Species_Mean, y = MaxLongevity_m))
g <- g + geom_point()
g <- g + geom_smooth(method = "lm", formula = y ~ x)
g <- g + geom_text(x=300, y = 300, label = " y = 1.218x + 248.952 ")
g
```

Alternative code that will also give the r-squared 
```{r}
df <- data.frame(x = data$Brain_Size_Species_Mean, y = data$MaxLongevity_m)
lm_eqn <- function(df){
    m <- lm(y ~ x, df);
    eq <- substitute(italic(y) == a + b %.% italic(x)*","~~italic(r)^2~"="~r2, 
         list(a = format(unname(coef(m)[1]), digits = 2),
              b = format(unname(coef(m)[2]), digits = 2),
             r2 = format(summary(m)$r.squared, digits = 3)))
    as.character(as.expression(eq));
}

p1 <- g + geom_text(x = 100, y = 800, label = lm_eqn(df), parse = TRUE)
p1
```

*nice!*

linear regression model for log model 

```{r}
longevity <- log(data$MaxLongevity_m)

brain.size <- log(data$Brain_Size_Species_Mean)

m2 <- lm(longevity ~ brain.size, data = data)
m2
```

use ggplot to graph model data 

```{r}
g <- ggplot(data = data, aes(x = brain.size, y = longevity))
g <- g + geom_point()
g <- g + geom_smooth(method = "lm", formula = y ~ x)
g <- g + geom_text(x=1.5, y = 6.25, label = " y = 0.2341x + 4.8790 ")
g
```

Alternative code: 

```{r}


df <- data.frame(x = brain.size, y = longevity)
lm_eqn <- function(df){
    m <- lm(y ~ x, df);
    eq <- substitute(italic(y) == a + b %.% italic(x)*","~~italic(r)^2~"="~r2, 
         list(a = format(unname(coef(m)[1]), digits = 2),
              b = format(unname(coef(m)[2]), digits = 2),
             r2 = format(summary(m)$r.squared, digits = 3)))
    as.character(as.expression(eq));
}

p1 <- g + geom_text(x = 1.5, y = 6.5, label = lm_eqn(df), parse = TRUE)
p1
```

Using the log function distributes the datapoints more evenly across the graph. This is a data transformation technique that can be used to make data fit the normal distribution, yes? 

Identify and interpret the point estimate of the slope (β1), as well as the outcome of the test associated with the hypotheses H0: β1 = 0; HA: β1 ≠ 0. Also, find a 90 percent CI for the slope (β1) parameter.

```{r}
x <- na.omit(data$Brain_Size_Species_Mean)
x
y <- na.omit(data$MaxLongevity_m)
y

beta1 <- sum((y - mean(y)) * (x - mean(x)))/sum((x - mean(x))^2)
beta1

beta0 <- mean(y) - beta1 * mean(x)
beta0

```

ci <- confint(beta1, level = 0.90)  
ci

The confint() function is givng me the error: $ operator is invalid for atomic vectors and I am not sure how to get around this 

